\documentclass{article}

\usepackage{geometry}
\usepackage{blindtext}
\usepackage{tabularx}
\usepackage{float}
\usepackage{titlesec}
\usepackage{verbatim}
\usepackage{amsmath}

\geometry{
    a4paper,
    left=15mm,
    right=15mm,
    top=15mm,
    bottom=15mm
}

\pagestyle{headings}

\begin{document}
    \begin{titlepage}
        \title{Common Application Settings Interface}
        \author{Studievereniging Sticky, MrFriendly B.V.}
        \date{2024\\Version 1.0.0}

        \maketitle
        \tableofcontents

        \pagebreak
    \end{titlepage}

    \section{Goal}
    \label{sec:goal}

    This specification describes a format for applications to retrieve
    settings from other applications in a standardized way.
    This allows applications to communicate with each other, and more importently,
    configure themselves to suit other applications.

    \subsection{Example: Scope managment}
    \label{subsec:example-scope-managment}

    A good example of when such a common interface is useful is
    authorization.
    An OAuth2 server can authorize a client to use specific scopes.
    But, to know about the scopes of the applications behind the OAuth2 application
    would require manual configuration.
    A standardized way of retrieving the list of available scopes would help in this situation.

    \subsection{Example: Settings page}
    \label{subsec:example-settings-page}

    Another good application is a common settings page.
    An application usually has some configuration parameters.
    One could build a settings page per application.
    But, better would be one settings page for all application.
    This specification describes methods for retrieving and setting such
    settings, allowing for one common page for everything.

    \section{Components}
    \label{sec:components}

    The common application settings interface (CASI) has multiple components to it:
    \begin{enumerate}
        \item General application information
        \item Supported scopes
        \item Application settings
        \item Deletion of user data (AVG)
    \end{enumerate}

    \section{General application information}
    \label{sec:general-application-information}
    \input{./tex/general_application_information}

    \section{Supported scopes}
    \label{sec:supported-scopes}
    \input{./tex/supported_scopes}

    \section{Application settings}
    \label{sec:application-settings}
    \input{./tex/application_settings}

    \section{Deletion of user data}
    \label{sec:deletion-of-user-data}
    \input{./tex/delete_user_data}

\end{document}